Incentivizing Exploration with Unbiased History

### 2018-11-02 intro-intro.tex
delineated recommendation vs disclosure policy

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, a line of work called {\em incentivizing exploration}.  One way to induce exploration is to introduce payments~\cite{}.  For example, an online retailer can give coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on {\em information asymmetry}~\cite{Kremer-JPE14}.  Here the idea is that the centralized algorithm can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.  These systems are often referred to as {\em recommendation systems} as the content of the message can be interpreted as a recommendation for a particular action.

>>>>

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.  In practice, such algorithms are often encountered in the form of recommendations.  One way to induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,Kempe-colt18}. For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.

### 2018-11-02 main.tex
clean up appendix C
adding authors
byebye bayesian
typo
main
delineated recommendation vs disclosure policy

% notation for 3level section
\newcommand{\conf}[1]{\mathtt{conf}\left(#1\right)}
\newcommand{\event}[1]{\ensuremath{\mathtt{event}_{#1}}\xspace}

@@

%index on the tap
\def\z{z}
\title{Incentivizing Exploration with Unbiased History}

\author{
}
\begin{document}
\begin{titlepage}
\maketitle

\thispagestyle{empty}
\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.  A sequence of agents each choose an action with the goal of maximizing payoff given estimates of the state of the world.  A recommendation algorithm tries to coordinate the choices of the agents by sending messages about the history of past actions.  The goal of the algorithm is to minimize the regret of the action sequence.

In this paper, we study a particular class of recommendation algorithms that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.  One trivial message of this form contains the full history; a recommendation algorithm that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a recommendation algorithm using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}

@@

\appendix
\input{prelim}
\input{app-warmup}
\input{3levelproofs}
\input{llevel}
\input{posterior}
\end{document}

>>>>

% notation for 3level section
\newcommand{\conf}[1]{\mathtt{conf}\left(#1\right)}
\newcommand{\event}[1]{\ensuremath{\mathtt{event}_{#1}}\xspace}
\newcommand{\cG}{\mathcal{G}}

@@

%index on the tape
\def\z{\tau}
\title{Incentivizing Exploration with Unbiased History}

\author{
Nicole Immorlica
\and
Jieming Mao
\and
Aleksandrs Slivkins
\and
Zhiwei Steven Wu
}
\begin{document}
\begin{titlepage}
\maketitle

\thispagestyle{empty}
\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.  A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.  A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.  The goal of the algorithm is to minimize the regret of the action sequence.

In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.  One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}

@@

\appendix
\input{prelim}
\input{app-warmup}
\input{3levelproofs}
\input{llevel}

%\input{posterior}
\end{document}
